### 2020-04-24 paper.tex
RxJS

\subsection{RxJS}

>>>>

\subsection{ReactiveX and RxJS}
Reactive Extensions is an open source project providing an API description for RP concepts. It describes itself as ``\dots a combination of the best ideas from the Observer pattern, the Iterator pattern, and functional programming'' \cite{reactivex}.  The API specification introduces the concept of the  \mintedinline{Observable} at its core. An \mintedinline{Observable} has the ability to be composed with other \mintedinline{Observable}s and eventually describe the dependency graph known in RP. A multitude of operators allow the transformation of values and \mintedinline{Observable}s within the graph.

The ReactiveX community works on a variety of reference implementations\footnote{\url{http://reactivex.io/languages.html}}: Libraries for Java, C#, JavaScript and many more allow to work with similar API semantics on different software architecture levels.

RxJS is the reference implementation for JavaScript. Its current major version 6 is completely done in TypeScript\footnote{\url{https://www.typescriptlang.org/}} and provides the core elements of the ReactiveX API specification. Large projects like Angular embed and use RxJS\cite{angularrxjs}. The Listing \ref{lst:rp-with-rxjs} shows a short example of RP using RxJS.
